Minimax lower bounds for source localization

### 2017-01-11 paper.tex
Add discussions; edit intro; fix +1 issue.

The source localization problem is one that appears in many fields where it is
of interest to find the position of a source (which emits some kind of signal)
using an array of sensors.

Our principal motivation comes from an application in brain activity
measurement, where one wishes to use modalities such as electroencephalography
(EEG) and magnetoencephalography (MEG) to record the activity inside the
brain~\cite{Baillet2001Electromagnetic}.  For example, current EEG systems use
anywhere between 10 and 250 sensors (electrodes), placed on the scalp, to sense
electric potentials produced by neuronal activity within the
brain~\cite{Nunez2006Electric}.

Recent developments~\cite{Grover2016Information} have suggested that source
localization can benefit greatly from an increase in sensor density. This
conclusion is based primarily on a Nyquist rate analysis, and on
information-theoretic bounds (which are possibly very loose) on the accuracy of
source localization algorithms. These bounds, first derived
in~\cite{Grover2016Fundamental}, do not capture scaling in number of sensors,
however, as the derivation effectively assumes the presence of an infinite
number of sensors to derive the bound.

Earlier work by Mosher et al.~\cite{Mosher1993Error}, which seeks to address
this issue by deriving Cramer-Rao lower bounds, is also not completely
satisfactory because these bounds do not apply to biased estimators. Commonly
used source localization algorithms (such as the Minimum Norm
Estimate~\cite{Hamalainen1994Interpreting}) on the other hand, are known to be
biased~\cite{Lin2006Assessing}.

@@

The one-dimensional toy problem is an effective tool for understanding bounds
on source localization accuracy in other settings as well, such as
\textcolor{red}{<insert other applications>}. A vast literature on linear
inverse problems (refer~\cite{Bal2012Introduction} for an introduction to this
field) and deconvolution algorithms exists, and has addressed the reduced
one-dimensional problem in broad settings
(see~\cite{Cavalier2002Sharp,Efromovich1997Robust,Ibragimov1981Statistical} and
references therein). However, our setting and interpretation appears to be
unique, since most prior work focuses on recovering a whole function (given
certain smoothness constraints), rather than locating a point source. Work that
does address point sources, to our knowledge, does not address scaling in the
number of sensors, since their problem setting and application is very
different.

Hence, we believe that this paper is the first to give lower bounds on source
localization error (measured in an $ell_2$-distance sense) in estimating the
location of a one-dimensional point source, which is observed by sensors
through a diffusive medium (treated as a low-pass filter), and corrupted by
additive Gaussian noise. We describe the problem setting in detail in
Section~\ref{sec:source-localization}, describe the minimax technique used and
give our main result in Section~\ref{sec:minimax-lower-bounds}, describe a few
straightforward extensions in Section~\ref{sec:extensions}, and conclude with a
discussion on implications for sensor placement and future work in
Section~\ref{sec:discussion}.

@@

We follow the excellent tutorial given in~\cite{Duchi2015Information} to
outline the preliminary steps in deriving bounds on the minimax risk.

@@

We start by lower bounding the minimax risk of the estimation problem with the
risk incurred in a multiple hypothesis testing problem. For this, we first need
to define a $2\delta$-packing:%
\begin{definition}
	A set $\Theta_{\mathcal{V}} = \{ \theta_v : v \in \mathcal{V} \}$ for some
	finite index set $\mathcal{V} \subset \mathbb N$ is said to be a
	$2\delta$-packing in the $\rho$-metric if $\rho(\theta_i, \theta_j) \geq
	2\delta \, \forall \, \theta_i, \theta_j \in \Theta_{\mathcal{V}}$.
\end{definition}
\begin{theorem} \label{thm:est-to-testing}%
	If we can find a $2\delta$-packing $\Theta_{\mathcal{V}}$ of $\Theta$, then
	we can lower bound the minimax estimation risk by the average testing risk:
	\begin{equation}
		\mathfrak{M}_n(\mathcal{P}, \Phiorho) \geq \Phi(\delta) \inf_\psi \mathbb P (\psi(Y^n) \neq V)
	\end{equation}
	where $V$ is the unknown, true hypothesis, and $\psi$ is our estimate of
	the hypothesis.
\end{theorem}
For a proof of this theorem, we refer the reader to Proposition~13.3
in~\cite{Duchi2015Information}.  Intuitively, Theorem~\ref{thm:est-to-testing}
says that the error in estimating $\theta_i$ is likely to be more if it is
difficult to distinguish $\theta_i$ from $\theta_j$, i.e.\ if the probability
of error is high (where $\theta_j$ has been selected to be suitably close).

@@

We now state the main result of this paper.
\begin{theorem}
	For a source localization problem as defined in
	section~\ref{sec:source-localization} with sensor noise and a spatial
	impulse response that is $\kappa$-Lipschitz continuous and has restricted
	support of width $w$, the asymptotic minimax risk in estimating the
	location of a point source is lower bounded by:
	\begin{equation}
		\mathfrak{M}_n(\mathcal{P}, \Phiorho) \geq \frac{1}{128} \frac{\sigma^2 T}{nm\kappa^2w}
	\end{equation}
\end{theorem}

@@

For the case of sensor noise, $P_i = \mathcal{N}(\v x(\theta_i), \sigma^2 \m
I)$, as described in section~\ref{sec:channel-model}. Hence, combining
equations~\eqref{eq:le-cam-bound}, \eqref{eq:pinsker-tensorization} and
\eqref{eq:kl-div-normal}, we see that
\begin{equation} \label{eq:lb-after-pinsker}
	\mathfrak{M}_n(\mathcal{P}, \Phiorho) \geq \frac{\delta^2}{2} \Bigg[ 1 - \sqrt{ \frac{n}{2\sigma^2} \norm*{\v x(\theta_0) - \v x(\theta_1)}^2 } \Bigg]
\end{equation}
Let $\v \Delta \overset{\text{def.}}{=} \v x(\theta_0) - \v x(\theta_1)$ for
brevity. Also, let $\Delta(k)$ denote the $k$-th element of $\v\Delta$, and
$\mathbb I_A(k)$ denote the indicator function of $k$ belonging to the set $A$
(i.e., $\mathbb I_A(k) = 1$ if $k \in A$, and is $0$ otherwise). Then, we have
\begin{align}
	&\norm{\v\Delta}^2 = \sum_{k=0}^{m-1} \abs{\Delta(k)}^2 = \sum_{k=0}^{m-1} \abs{\Delta(k)}^2 \, \mathbb I_{\{\ell: \abs{\Delta(\ell)} > 0\}}(k) \\
	&= \sum_{k=0}^{m-1} \abs[\Big]{x\Big(\frac{kT}{m}; \theta_0\Big) - x\Big(\frac{kT}{m}; \theta_1\Big)}^2 \mathbb I_{\{\ell: \abs{\Delta(\ell)} > 0\}}(k) \\
	&= \sum_{k=0}^{m-1} \abs[\Big]{g\Big(\frac{kT}{m} - \theta_0\Big) - g\Big(\frac{kT}{m} - \theta_1\Big)}^2 \mathbb I_{\{\ell: \abs{\Delta(\ell)} > 0\}}(k)
\end{align}
where $x(t;\theta_i)$ is the continuous-space filtered signal described in
section~\ref{sec:signal-model}. For an impulse response $g$ which is Lipschitz
continuous with parameter $\kappa$, we can upper bound the term within the
summation:
\begin{equation}
	\abs[\Big]{g\Big(\frac{kT}{m} - \theta_0\Big) - g\Big(\frac{kT}{m} - \theta_1\Big)} \leq \kappa \abs{\theta_0 - \theta_1} = \kappa \cdot 2\delta
\end{equation}
since $\abs{\theta_0 - \theta_1} = 2\delta$ by virtue of the $2\delta$ packing.
Hence,
\begin{equation}
	\norm{\v\Delta}^2 \leq 4 \kappa^2 \delta^2 \sum_{k=0}^{m-1} \mathbb I_{\{\ell: \abs{\Delta(\ell)} > 0\}}(k) = 4 \kappa^2 \delta^2 \norm{\v\Delta}_0.
\end{equation}
$\norm{\v\Delta}_0$ is the number of non-zero elements in $\v\Delta$, which is
equal to the number of sensors in the total region covered by the signals
$x(t;\theta_0)$ and $x(t;\theta_1)$ (see Figs.~\ref{fig:overlap-middle} and
\ref{fig:delta-sampled}). Therefore, $\norm{\v\Delta}_0 = \floor[\big]{\frac{(w
+ 2\delta)m}{T} + 1}$, since at most a fraction $(w + 2\delta) / T$ of the $m$
sensors (plus 1, to account for edge-effects) can lie in the region covered by
the two impulse responses. The final upper bound on $\norm{\v\Delta}^2$ is
hence
\begin{equation} \label{eq:delta-bound}
	\norm{\v\Delta}^2 \leq 4 \kappa^2 \delta^2 \floor*{\frac{(w + 2\delta)m}{T} + 1} \leq 4 \kappa^2 \delta^2 \Big(\frac{(w + 2\delta) m}{T} + 1\Big).
\end{equation}
Since sensors are uniformly distributed, and since the domain is periodic, this
holds even if $\theta_0$ lies at the edge of the domain (close to $t=0$, for
example). In such a case, one part of the signal $x(t;\theta_0)$ will appear at
the left edge of the domain, and the repetition from the period $[T, 2T)$ will
appear at the right edge of the domain. Also note that the two signals
$x(t;\theta_0)$ and $x(t;\theta_1)$ overlap at most once, since $w < T/2$, as
stated in section~\ref{sec:signal-model}.

The upper bound in~\eqref{eq:delta-bound} translates into a lower
bound for~\eqref{eq:lb-after-pinsker}:
\begin{align}
	\mathfrak{M}_n(\mathcal{P}, \Phiorho) &\geq \frac{\delta^2}{2} \Bigg[ 1 - \sqrt{\frac{n}{2\sigma^2 T} 4 \kappa^2 \delta^2 (w + 2\delta) m} \Bigg] \\
	&= \frac{\delta^2}{2} \Bigg[ 1 - \sqrt{\frac{2nm \kappa^2 \delta^2 (w + 2\delta)}{\sigma^2 T}} \Bigg] \label{eq:lb-after-delta-bound}
\end{align}
Asymptotically, we choose smaller values of $\delta$ for larger number of
sensors. Hence, neglecting terms of order $\delta^3$, we tighten the bound by
choosing $\delta$ as a function of the remaining variables in order to have
$\sqrt{\frac{2nm\kappa^2\delta^2 w}{\sigma^2 T}} = \frac{1}{2}$. This is
achieved for $\delta = \sqrt{\frac{\sigma^2T}{8nm\kappa^2 w}}$, so that for
$\Phi(\delta) = \delta^2$, equation~\eqref{eq:lb-after-delta-bound} becomes
\begin{equation}
	\mathfrak{M}_n(\mathcal{P}, \Phiorho) \geq \frac{1}{128} \frac{\sigma^2 T}{nm\kappa^2 w}.
\end{equation}
This completes the proof.
\end{IEEEproof}

@@

We can trivially expand the domain of impulse responses to which the lower
bound applies to include $\alpha$-Holder continuous functions. These are
functions which satisfy
\begin{equation}
	\abs{g(u) - g(v)} \leq \kappa \norm{u - v}^\alpha \, \forall \, u, v \in \text{dom} \; g
\end{equation}
for some constant $\kappa$, and for $\alpha > 0$.

@@

\textcolor{red}{Needs rewrite.}

The reason that the local Fano method gives a poorer bound than Le Cam's method
is that we're using the local Fano method on a bounded domain, making $V$ as a
function of the packing size $\delta$.  It is evident even from examining
equations \eqref{eq:fano-lb} and \eqref{eq:mutual-info-kl-reln} that taking
just two hypotheses with a suitable separation will yield tighter bounds, since
the cardinality of the packing set $V$ will no longer be dependent on $\delta$.
This will allow us to make use of the expression in equation
\eqref{kl-vi-vj-final} to choose $\delta$, which will yield the rate we saw in
Le Cam's method. It is to be seen whether using the global Fano
method~\cite{Duchi2015Information} will improve the rate, or at least, the
constants that we attained with Le Cam's technique. A more rigorous treatment,
which finds an upper bound for the sum, rather than using integrals, so as to
give bounds for even moderate numbers of sensors is also delegated to future
work.

>>>>

The source localization problem is one that appears in many fields where it is
of interest to find the position of a source using an array of sensors.

Our principal motivation comes from an application in brain activity
measurement, where one wishes to use modalities such as electroencephalography
(EEG) and magnetoencephalography (MEG) to record activity inside the
brain~\cite{Baillet2001Electromagnetic}.  For example, current EEG systems use
anywhere between 10 and 250 sensors (electrodes) placed on the scalp, to sense
electric potentials produced by neuronal activity within the
brain~\cite{Nunez2006Electric}. The neurons (or groups of neurons) which
produce this activity are frequently modeled as current dipoles. For a single
activated dipole within the brain (which is modeled as being localized to a
point), the electrodes effectively sense a diffuse (blurred-out) representation
of the point source, as a result of the spatial low-pass filtering effect of
the different layers between the brain surface and scalp surface (cerebrospinal
fluid, skull and skin).

Recent developments~\cite{Grover2016Information} have suggested that source
localization can benefit greatly from an increase in sensor density. This
conclusion is based primarily on a Nyquist rate analysis, and on an
information-theoretic bound (which are possibly very loose) on the accuracy of
source localization algorithms. In deriving this bound, however, the scalp
potential was never sampled; equivalently, it was assumed that an
\emph{infinite} number of sensors was available to sample the EEG signal at
every point on the scalp. Hence, the dependence of the bound on the number of
sensors is lost.

Earlier work by Mosher et al.~\cite{Mosher1993Error}, which seeks to address
this issue by deriving Cramer-Rao lower bounds, is also not completely
satisfactory because these bounds do not apply to biased estimators. Commonly
used source localization algorithms (such as the Minimum Norm
Estimate~\cite{Hamalainen1994Interpreting}) on the other hand, are \emph{known}
to be biased~\cite{Lin2006Assessing}.

@@

The one-dimensional toy problem is an effective tool for understanding bounds
on source localization accuracy in other settings as well, such as
\textcolor{red}{<insert other applications>}. A vast literature on linear
inverse problems (see~\cite{Bal2012Introduction} for an introduction to this
field) and deconvolution algorithms exists, and has addressed the reduced
one-dimensional problem in broad settings
(see~\cite{Cavalier2002Sharp,Efromovich1997Robust,Ibragimov1981Statistical} and
references therein). However, our setting and interpretation appears to be
unique, since most prior work focuses on recovering a whole function (given
certain smoothness constraints), rather than locating a point source. Work that
does address point sources, to our knowledge, does not address scaling in the
number of sensors, since problem settings and applications differ greatly.

Hence, we believe that this paper is the first to give lower bounds on source
localization error (measured in an $\ell_2$-distance sense) in estimating the
location of a one-dimensional point source, which is observed by sensors
through a diffusive medium (treated as a low-pass filter), and corrupted by
additive Gaussian noise. We describe the problem setting in detail in
Section~\ref{sec:source-localization}, the minimax techniques and our main
result in Section~\ref{sec:minimax-lower-bounds} and a few straightforward
extensions in Section~\ref{sec:extensions}. Finally, we conclude with a
discussion on implications for sensor placement and future work in
Section~\ref{sec:discussion}.

@@

\textcolor{blue}{
Several techniques for deriving lower bounds on the minimax risk are described
in~\cite{Tsybakov2009Introduction}. We follow the excellent tutorial written by
John Duchi~\cite{Duchi2015Information} to briefly outline the steps involved in
deriving these bounds.
}

@@

We start by lower bounding the minimax risk of the estimation problem with the
risk incurred in a multiple hypothesis testing problem. For this, we first need
to define a $2\delta$-packing:%
\begin{definition}
	A set $\Theta_{\mathcal{V}} = \{ \theta_v : v \in \mathcal{V} \}$ for some
	finite index set $\mathcal{V} \subset \mathbb N$ is said to be a
	$2\delta$-packing in the $\rho$-metric if
	\begin{equation}
		\rho(\theta_i, \theta_j) \geq 2\delta \qquad \forall \;\; \theta_i, \theta_j \in \Theta_{\mathcal{V}}.
	\end{equation}
\end{definition}
\begin{theorem} \label{thm:est-to-testing}%
	If we can find a $2\delta$-packing $\Theta_{\mathcal{V}}$ of $\Theta$, then
	we can lower bound the minimax estimation risk by the average testing risk:
	\begin{equation}
		\mathfrak{M}_n(\mathcal{P}, \Phiorho) \geq \Phi(\delta) \inf_\psi \mathbb P (\psi(Y^n) \neq V)
	\end{equation}
	where $V$ is the unknown, true hypothesis, and $\psi$ is our estimate of
	the hypothesis.
\end{theorem}
For a proof of this theorem, we refer the reader to Proposition~13.3
in~\cite{Duchi2015Information}.  Intuitively, Theorem~\ref{thm:est-to-testing}
says that the error in estimating $\theta_i$ is likely to be more if it is
difficult to distinguish $\theta_i$ from $\theta_j$, i.e.\ if the probability
of error is high (where $\theta_j$ has been selected to be suitably close).

@@

We now state the main result of this paper.
\begin{theorem} \label{thm:main-lb}
	For a source localization problem as defined in
	section~\ref{sec:source-localization} with sensor noise and a spatial
	impulse response that is $\kappa$-Lipschitz continuous and has restricted
	support of width $w$, the \textcolor{blue}{asymptotic} minimax risk in estimating the
	location of a point source is lower bounded by:
	\begin{equation} \label{eq:main-lower-bound}
		\mathfrak{M}_n(\mathcal{P}, \Phiorho) \geq \frac{1}{128} \frac{\sigma^2 T}{nm\kappa^2w}
	\end{equation}
\end{theorem}

@@

For the case of sensor noise, $P_i = \mathcal{N}(\v x(\theta_i), \sigma^2 \m
I)$, as described in section~\ref{sec:channel-model}. Hence, combining
equations~\eqref{eq:le-cam-bound}, \eqref{eq:pinsker-tensorization} and
\eqref{eq:kl-div-normal}, we see that
\begin{equation} \label{eq:lb-after-pinsker}
	\mathfrak{M}_n(\mathcal{P}, \Phiorho) \geq \frac{\delta^2}{2} \Bigg[ 1 - \sqrt{ \frac{n}{2\sigma^2} \norm*{\v x(\theta_0) - \v x(\theta_1)}^2 } \Bigg]
\end{equation}
Let $\v \Delta \overset{\text{def.}}{=} \v x(\theta_0) - \v x(\theta_1)$ for
brevity. Also, let $\Delta(k)$ denote the $k$-th element of $\v\Delta$, and
$\mathbb I_A(k)$ denote the indicator function of $k$ belonging to the set $A$
(i.e., $\mathbb I_A(k) = 1$ if $k \in A$, and is $0$ otherwise). Then, we have
\begin{align}
	&\norm{\v\Delta}^2 = \sum_{k=0}^{m-1} \abs{\Delta(k)}^2 = \sum_{k=0}^{m-1} \abs{\Delta(k)}^2 \, \mathbb I_{\{\ell: \abs{\Delta(\ell)} > 0\}}(k) \\
	&= \sum_{k=0}^{m-1} \abs[\Big]{x\Big(\frac{kT}{m}; \theta_0\Big) - x\Big(\frac{kT}{m}; \theta_1\Big)}^2 \mathbb I_{\{\ell: \abs{\Delta(\ell)} > 0\}}(k) \\
	&= \sum_{k=0}^{m-1} \abs[\Big]{g\Big(\frac{kT}{m} - \theta_0\Big) - g\Big(\frac{kT}{m} - \theta_1\Big)}^2 \mathbb I_{\{\ell: \abs{\Delta(\ell)} > 0\}}(k)
\end{align}
where $x(t;\theta_i)$ is the continuous-space filtered signal described in
section~\ref{sec:signal-model}. For an impulse response $g$ which is Lipschitz
continuous with parameter $\kappa$, we can upper bound the term within the
summation:
\begin{equation}
	\abs[\Big]{g\Big(\frac{kT}{m} - \theta_0\Big) - g\Big(\frac{kT}{m} - \theta_1\Big)} \leq \kappa \abs{\theta_0 - \theta_1} = \kappa \cdot 2\delta
\end{equation}
since $\abs{\theta_0 - \theta_1} = 2\delta$ by virtue of the $2\delta$ packing.
Hence,
\begin{equation}
	\norm{\v\Delta}^2 \leq 4 \kappa^2 \delta^2 \sum_{k=0}^{m-1} \mathbb I_{\{\ell: \abs{\Delta(\ell)} > 0\}}(k) = 4 \kappa^2 \delta^2 \norm{\v\Delta}_0.
\end{equation}
$\norm{\v\Delta}_0$ is the number of non-zero elements in $\v\Delta$, which is
equal to the number of sensors in the total region covered by the signals
$x(t;\theta_0)$ and $x(t;\theta_1)$ (see Figs.~\ref{fig:overlap-middle} and
\ref{fig:delta-sampled}). Therefore, $\norm{\v\Delta}_0 = \floor[\big]{\frac{(w
+ 2\delta)m}{T} + 1}$, since at most a fraction $(w + 2\delta) / T$ of the $m$
sensors \textcolor{blue}{(plus 1, to account for edge-effects)} can lie in the region covered by
the two impulse responses. The final upper bound on $\norm{\v\Delta}^2$ is
hence
\begin{equation} \label{eq:delta-bound}
	\norm{\v\Delta}^2 \leq 4 \kappa^2 \delta^2 \floor*{\frac{(w + 2\delta)m}{T} + 1} \leq 4 \kappa^2 \delta^2 \Big(\frac{(w + 2\delta) m}{T} + 1\Big).
\end{equation}
Since sensors are uniformly distributed, and since the domain is periodic, this
holds even if $\theta_0$ lies at the edge of the domain (close to $t=0$, for
example). \textcolor{blue}{In such a case, one part of the signal $x(t;\theta_0)$ will appear at
the left edge of the domain, and the remaining part will appear as the
repetition from the period $[T, 2T)$, at the right edge of the domain.} Also
note that the two signals $x(t;\theta_0)$ and $x(t;\theta_1)$ overlap at most
once, since $w < T/2$, as stated in section~\ref{sec:signal-model}.

The upper bound in~\eqref{eq:delta-bound} translates into a lower
bound for~\eqref{eq:lb-after-pinsker}:
\begin{align}
	\mathfrak{M}_n(\mathcal{P}, \Phiorho) &\geq \frac{\delta^2}{2} \Bigg[ 1 - \sqrt{\frac{n \cdot 4 \kappa^2 \delta^2}{2\sigma^2} \bigg( \frac{(w + 2\delta) m}{T} + 1\bigg)} \Bigg] \\
	&= \frac{\delta^2}{2} \Bigg[ 1 - \sqrt{\frac{2n \kappa^2 \delta^2}{\sigma^2} \bigg( \frac{(w + 2\delta) m}{T} + 1\bigg)} \Bigg] \label{eq:lb-after-delta-bound}
\end{align}
Asymptotically, we choose smaller values of $\delta$ as the number of sensors
grows large. Hence, \textcolor{blue}{neglecting edge effects} and terms of order $\delta^3$, we
tighten the bound by choosing $\delta$ as a function of the remaining variables
in order to have $\sqrt{\frac{2nm\kappa^2\delta^2 w}{\sigma^2 T}} =
\frac{1}{2}$. This is achieved for $\delta = \sqrt{\frac{\sigma^2T}{8nm\kappa^2
w}}$, so that for $\Phi(\delta) = \delta^2$,
equation~\eqref{eq:lb-after-delta-bound} becomes
\begin{equation}
	\mathfrak{M}_n(\mathcal{P}, \Phiorho) \geq \textcolor{blue}{\frac{1}{32}} \frac{\sigma^2 T}{nm\kappa^2 w}.
\end{equation}
This completes the proof.
\end{IEEEproof}

@@

We can trivially expand the domain of impulse responses to which the lower
bound in~\eqref{eq:main-lower-bound} applies to include $\alpha$-Holder
continuous functions. These are functions which satisfy
\begin{equation}
	\abs{g(u) - g(v)} \leq \kappa \abs{u - v}^\alpha \, \forall \, u, v \in \text{dom} \; g
\end{equation}
for some constant $\kappa$, and for $\alpha > 0$. Using this property,
equation~\eqref{eq:delta-bound} reads
\begin{equation} \label{eq:holder-delta-bound}
	\norm{\v\Delta}^2 \leq \kappa^2 (2 \delta)^{2\alpha} \bigg(\frac{(w + 2\delta) m}{T} + 1\bigg).
\end{equation}
Hence, we choose $\delta = (\frac{\sigma^2 T}{2^{2\alpha + 1} nm \kappa^2
w})^{1/2\alpha}$, to procure an asymptotic lower bound
\begin{equation}
	\mathfrak{M}_n(\mathcal{P}, \Phiorho) \geq \frac{1}{4} \bigg(\frac{\sigma^2 T}{2^{2\alpha + 1} nm \kappa^2
w}\bigg)^{1/\alpha}.
\end{equation}

@@

The lower bound given by Theorem~\ref{thm:main-lb} goes to zero as the number
of sensors, $m$, goes to infinity, \emph{even if} the total number of trials
$n$ is kept \emph{fixed}. This would mean that a high sensor density can
overcome the effect of noise in a single trial. The reason this happens is that
we assume sensors are affected by i.i.d. noise, no matter what sampling density
we use. This is an increasingly poor assumption as sensor density increases,
however; we expect noise to become correlated if sensors are extremely close
(due to inductive/capacitive coupling, for example). A more realistic lower
bound will show the benefit of increasing sensor density up to a point only,
beyond which it will have to scale alongside the number of trials.

The lower bounding \emph{technique} gives certain inisights on the issue of
sensor placement. Suppose we wanted to achieve a higher resolution in a
restricted interval of the parameter space, i.e.\ $\theta \in [a, b] \subset
\Theta$, such that $\abs{b - a} \ll w$. Then, it might be of greatest benefit
to place sensors \emph{not} precisely over the region, but rather in the region
corresponding to the \emph{largest change} in the impulse response. Indeed, it
is possible to derive an  approximate lower bound using Taylor's approximation,
which shows that the KL-divergence between distributions is maximized (and
hence error minimized) at regions where the slope of $x(t;\theta)$ is largest.

Another point on sensor placement bears repeating: the bounds derived in this
paper apply to only a specific sensor configuration, i.e., the uniform one.
This would intuitively seem to be an appropriate choice in the minimax setting,
however, since any non-uniform placement will have one or more points which is
far from all sensors. The ``maximization'' over $\theta \in \Theta$ would then
select such a point, where the value of the impulse response so produced at the
sensors is smallest, so that SNR is minimized.

For the application of EEG source localization, it might be possible to find
algorithms which achieve similar scalings as the lower bounds presented here.
It is also hoped that the techniques presented here will help us derive
analytical bounds in the more difficult setting.

\section*{Acknowledgements}

Praveen Venkatesh is partially supported by the Dowd Fellowship from the
College of Engineering at Carnegie Mellon University. The authors would like to
thank Philip and Marsha Dowd for their support and encouragement.
